Untitled

### 2024-08-26 code/manuscript_analysis.Rmd
windsorize data when poor quality, lots of variation due to noise (total hours of access, efficiency)

did2s(
      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.87) & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

>>>>

did2s(
      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))), 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

did2s(
      data = df.spill3  %>% filter((Dist < quantile(Dist, 0.15) & Att > 0) | Att == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))), 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
